\begin{abstract} 

    \noindent We are developing a ZK-ZKVM platform for \cite{website:Ethereum} that will offer the following features: 
    (1) Programmable Privacy: Supporting a vast variety of privacy design options for smart contracts. dApp developers can choose to deploy protocols, and users can use these dApps to send transactions both publically and privately according to their needs.
    (2) High Programmability: Supporting ISA-based smart contract languages and allows developers to compile arbitrary logic.
    (3) High Performance: Our full-featured zk-friendly ZKVM, OlaVM \cite{website:OlaVM}, can quickly execute transactions and generate proofs.
    (4) Developer-friendly smart contract language: Ola-lang \cite{website:Ola-lang}  is customized for smart contract development with syntax similar to Rust, making it convenient for developers quickly adopt it.
    (5) External Integrations: Ola-lang language is integrated into the IDE Visual Studio Code, making it convenient for traditional developers to start building.
    (6) Better Scalability: Based on the LLVM compilation framework, it is easier to achieve compatibility with other high-level languages, such as Solidity \cite{website:Solidity}.
    (7) Robust Architecture: Through the means of viewing keys which can be shared to third parties, we create a compliance-friendly landscape, providing the possibillity to, example given, regulators to track the actual whereabouts of private assets, avoidong the disadvantages of untraceable assets, such as Tornado Cash \cite{website:Tornado-cash}.
    (8) Flexible Data Sharing: Indefinitely exposing your viewing key to a third party allows for continouous monitoring and tracking of an accounts status.
    (9) Empowering Users: Returning the control of their own asset information and on-chain data, in an unpermissioned and private state at the hands of the end user. 
    \\ \hspace*{\fill} \\
    \noindent Ola is a rapidly developing project, our second iteration of the Whitepaper further details the design philosophy and specifications of our full featured and efficient ZKVM, 
    OlaVM \cite{website:OlaVM} and developer-friendly general purpose smart contract language, Ola-lang \cite{website:Ola-lang}. Implementation details related to privacy will be released in the upcoming third iteration of the whitepaper upon releasing testnet.
    \\ \hspace*{\fill} \\
    \noindent \textbf{Key words: Privacy, Programmability, ZKVM, Smart contract, Data ownership.}    
\end{abstract}