\section{ZK-ZKVM} \label{sec:zk-zkvm}

A ZK-VM \ref{sec:ola-vm-a-full-featured-zk-friendly-zkvm} which is a system that uses zk technology to implement a verifiable circuit system for general computation. However, it has some issues where privacy is required, for example, quotation data of commercial competition, anonymous auction, etc. The generation of each program's proof executed in the ZK-VM leaks the witness data, such as the name and function of the called contract, parameters, and so on.

To address this privacy concern, the ZK-ZKVM system has been developed. This system builds on top of ZK-VM but adds an extra layer of privacy by ensuring that all witness data is private and does not reveal any information. This is achieved through the use of a key system consists of different permissioned private keys and a note mechanism similar to ZCash's UTXO model.

The basic principle of ZK-ZKVM is the use of different permissioned private keys in the key system. These keys are used to encrypt and decrypt the witness data, ensuring that it remains private and secure. Additionally, the note mechanism is used to further enhance the privacy of the system. Each note represents a certain amount of value that is spendable by the recipient, and is transmitted in ciphertext. It is impossible to deduce any information about the transaction from this ciphertext.

The importance of ZK-ZKVM lies in its ability to address the privacy concerns that exist in ZK-VM. With ZK-ZKVM, users can conduct transactions on public blockchains with the assurance that their sensitive information is secure and private. This makes it suitable for a wide range of use cases that require high levels of privacy, such as financial transactions or data sharing.

Furthermore, ZK-ZKVM also offers the same scalability benefits as ZK-VM. By allowing for off-chain computation and verification, it reduces the burden on the main blockchain and increases transaction throughput. This makes it a more efficient and effective solution for blockchain scaling than traditional solutions.

In Section \ref{section: zk-zkvm-key}, we provide an in-depth explanation of the key system design in our ZK-ZKVM system. In the following section, Section \ref{section: zk-zkvm-note}, we explore the note design within our ZK-ZKVM system. Moving on, in Sections \ref{section: zk-zkvm-user-end-prove} and \ref{section: zk-zkvm-delegable-prove}, we conduct a comparative analysis of two distinct approaches to proof generation. Finally, in Section \ref{section: zk-zkvm-framework}, we present the fundamental framework of ZK-ZKVM.

\input{zk-zkvm/key}
\input{zk-zkvm/note}
\input{zk-zkvm/user-end-prove}
\input{zk-zkvm/delegable-prove}
\input{zk-zkvm/framework}