\section{Introduction}\label{sec:introduction}

In the past few years, we have witnessed a rapid development of the blockchain industry, influx of capital, users, and builders has enabled unprecedented growth and potential of the entire industry. However, blockchain is still somewhat in its infancy, infrastructure is still maturing. One of the largest challenges is the low transactional throughput of public blockchain systems, especially the largest public programmable blockchain Ethereum \cite{website:Ethereum}, which in the best case scenario \cite{website:Etherscan-chart}, processes up to 23 transactions per second, far less than traditional centralized systems. 

There are many reasons for the congestion of the Ethereum network, such as the POW \cite{website:POW} consensus algorithm (The Merge upgrade \cite{website:The-Merge} to POS \cite{website:POS} consensus now), the repeated execution of verification process of all transactions by nodes, and the serial execution of transactions; for the above reasons, many projects are trying to scale Ethereum through different means. Approach 1: Launching new public blockchains, independent of Ethereum, using faster consensus algorithms or faster transaction execution to achieve higher TPS, such as BSC \cite{website:BSC}, Solana \cite{website:Solana}, Aptos \cite{website:Aptos}, etc; Approach 2: Ethereum Sidechain, using faster consensus algorithms and then regularly synchronizing to Ethereum, such as Polygon \cite{website:Polygon}, Optimism \cite{website:Optimism}, Arbitrum \cite{website:Arbitrum}, etc; Approach 3: ZK(E)VM, a Layer2 network of Ethereum, using ZK technology to solve the problem of repeated execution of transactions, such as Polygon Hermez \cite{website:Polygon-Hermez}, Zksync \cite{website:Zksync} etc.

Scaling is not the only problem that has to be solved in the long term for Ethereum and the wider blockchain space. There are many excellent teams working rigorously on scaling solutions, the ola team believe that the next crucial feature to be implemented is privacy. Blockchains being a public ledger, all transactions taking place on-chain, meaning state changes containing the asset information related to an address or account is open and transparent. 

Excessive information transparency leads to: 

\begin{enumerate}
    \item MEV (Maximal Extractable Value) issues. Miners can selectively package transactions based on its fee, resulting in transactions with lower fees having a lower likelihood of being processed, if ever, forcing users to increase their fees. More concerning:
    \item Front running and censorship attacks, through the means of MEV. Block producers in programmable blockchains can use MEV to exploit certain smart contracts deployed on the blockchain (Such as DEXes and other DeFi products). They may also censor certain addresses. Such an attack could be that the miner or block producer sees a buy order in the memory pool (where transactions that are not yet appended to the blockchain are stored) and adds their own buy order on that particular DEX, thus increasing the price of the given token. The other transaction that is added is a sell order of given token and the third order is the buy order of the third party for the new increased price. Resulting in huge security issues and in the past year hackers have managed to steal assets roughly amounting to 2 billion dollars.
    \item User data ownership problems, both the assets information and transaction information of addresses are open to being monitored and used, which is contrary to the vision of Web3 \cite{website:Web3}. Therefore, when the scaling problem is solved, privacy will become the next urgent feature to achieve. In the world of blockchain, privacy is not a new topic, it has long been studied and supported by the Zcash team \cite{website:Zcash}.
\end{enumerate}

\input{introduction/non programmable privacy}
\input{introduction/programmable privacy}
\input{introduction/full-featured zk-friendly zkvm}
\input{introduction/outline}
