\section{Algorithms} \label{sec:algorithms}
Ola uses zero-knowledge proof technologies to ensure the correct execution of the program and protect privacy. Zero-knowledge proof technologies enable one party to prove to another party that a statement is true without revealing any additional information. 

Two of the most compelling zero-knowledge technologies on the market today are zk-STARK and zk-SNARK. Zk-SNARK stands for Zero-Knowledge Succinct Non-interactive Argument of Knowledge. They were introduced in a \href{https://dl.acm.org/doi/10.1145/2090236.2090263}{2012 paper} co-authored by Nir Bitansky, Ran Canetti, Alessandro Chiesa, and Eran Tromer. Zk-STARK stands for Zero-Knowledge Scalable Transparent Argument of Knowledge and is a zero-knowledge proof system that was introduced as an alternative to SNARKs in a \href{https://starkware.co/wp-content/uploads/2022/05/STARK-paper.pdf}{2018 paper} by Eli Ben-Sasson, Iddo Bentov, Yinon Horesh, and Michael Riabzev. We have a table depicting some of the high-level differences between the two technologies.

\begin{table}[!ht]
    \centering
    \begin{tabular}{|l|l|l|}
        \hline
                            & zk-SNARK    & zk-STARK                   \\
        \hline
        Proving complexity   & $O(N\log(N))$ & $O(N\mathrm{polylog}(N))$            \\
        \hline
        Verifying complexity & $O(1)$        & $O(\mathrm{polylog}(N))$              \\
        \hline
        Proof size           & $O(1)$        & $O(\mathrm{polylog}(N))$              \\
        \hline
        Trusted setup        & YES         & NO                         \\
        \hline
        Quantum resistant    & NO          & YES                        \\
        \hline
        Crypto assumptions   & Strong      & Collision resistant hashes \\
        \hline
    \end{tabular}
\end{table}

\noindent The advantage of zk-STARK is that
\begin{enumerate}
    \item Lower gas (more scalable)
    \item Larger batch size (more scalable)
    \item Faster proofs (more scalable)
    \item No trusted setup (the generated parameters are only valid for the current application, if there are changes, you need to re-setup)
    \item Post-quantum secure
\end{enumerate}

However, the proof generated by zk-STARK is larger, and due to some limitations such as WASM, additional operations are required to turn the zk-STARK proof into a zk-SNARK proof during construction.
    
\input{algorithms/starky/main}
\input{algorithms/plonky2/main}
\input{algorithms/inner-table-lookup}
\input{algorithms/cross-table-lookup}
\input{algorithms/gpu-acceleration}
\input{algorithms/fpga-acceleration}
