\subsubsection{ISA description: register and insts}

\begin{itemize}
    \item back-end codegen modules

bridging ir structure of module, function, and isa related callconv, register and isa, code generation related lower and optimization related pass.

TargetISA main contains custom TargetInst, Register(RegisterClass/RegisterInfo), lower and modulepasses, callconv, datalayout information.

Module in addition to inheritance Ir parsed out Module, the description of its Function and ir differ significantly.

Data information: BasicBlock in the instructions for Target Instruction, register contains VRegs and RegUnit two categories, and contains a vregtoinsts mapping.
At the same time, Inst in Layout are referred to TargetInst. Note that the memory access operations of parameters, local variables, etc. are described by the structure of slot(ptr+offset).

The lower module provides the process of downgrading LoweringContext to Instruction, and for function calls it also requires copyargstovregs.

The pass module contains the regalloc and spiller for analyzing the liveness of the pass and the function pass.

        \item back-end process

(1) Register and insts description

Register description is as below:
\begin{table}[!ht]
    \resizebox{\textwidth}{!}{
        \begin{tabular}{|c|c|c|}
            \hline
            \textit{Type}  & \textit{Description} & \textit{Register Group}  \\ \hline
            general registers & general used by program &  $[r0-r8] $ \\ \hline
            return regsiter & return value for return to caller &  $[r0] $ \\ \hline
            parameters rigsters & parameters value for passing arguments &  $ [r1, r2, r3] $ \\ \hline
            tmp registers & tmp alloc for local variables &  $[r4, r5, r6, r7]$ \\ \hline
            stack pointer & function's stack pointer &  $[r8] $ \\ \hline
            special registers & interact with vm: pc for program counter and psp for prophet pointer &   $[pc, psp] $ \\ \hline
        \end{tabular}}
    \caption{Register Description}
    \label{table:register-description}
\end{table}

Insts description is as bellow:

Opcode with register or immdiate number:
\begin{lstlisting}[language={}]
    ADDri,
    ADDrr,
    MULri,
    MULrr,

    EQri,
    EQrr,
    ASSERTri,
    ASSERTrr,

    MOVri,
    MOVrr,

    JMPi,
    JMPr,
    CJMPi,
    CJMPr,
    CALL,
    RET,
    END,

    MLOADi,
    MLOADr,
    MSTOREi,
    MSTOREr,

    RANGECHECK,
    AND,
    OR,
    XOR,
    NOT,
    NEQ,
    GTE,

    PROPHET,

    Phi,
\end{lstlisting}

Operand data type:
\begin{lstlisting}[language={}]
    Reg(Reg),
    VReg(VReg),
    Int8(i8),
    Int32(i32),
    Int64(i64),
    MemStart,
    Slot(SlotId),
    Block(BasicBlockId),
    Label(String),
    GlobalAddress(String),
    None,
\end{lstlisting}

\end{itemize}